---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width=6, fig.height=3.5,
  fig.showtext = TRUE,dpi = 300)
```

# idstyle

<!-- badges: start -->
[![R-CMD-check](https://github.com/wf-id/idstyle/workflows/R-CMD-check/badge.svg)](https://github.com/wf-id/idstyle/actions)
<!-- badges: end -->

The goal of idstyle is to ...

## Installation

You can install the development version of idstyle like so:

``` r
remotes::install_github("wf-id/idstyle")
```

## Examples

### Tables

Flextable formatting:

 - Black & white (default)

```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(idstyle))
head(mtcars) |> format_flex_table() 
```

 - "wake" color
 
```{r}
head(mtcars) |> format_flex_table(color = 'wake') 
```

### Plots


 - Points with wake gold default
 
```{r}
ggplot(mtcars, aes(x = mpg, y = hp)) +
  geom_point(aes(color = carb))
```

 - Wake color palette for factors

```{r}
ggplot(mtcars) + geom_bar(aes(x = carb, fill = factor(carb)))
```

 - Label formatting
 
```{r}
gg2 <- mtcars |> ggplot(aes(x = mpg, y = hp, color = cut(mtcars$hp,6))) + #discrete scale
  geom_point() + labs(title = 'This is a title for my graph',
                      subtitle = 'This is a subtitle for my graph',
                      caption = 'This is a caption for my graph',
                      color = 'HP')
gg2
```

 - Grids
 
```{r}
gg2 + theme_wake(grid = 'both') +
  labs(title = 'Now with grids!')
```

 - Facets

```{r}
gg2 + facet_wrap(~gear) + theme_wake_facet(grid = 'y') +
  labs(title = 'Some facets! And y grids only')

```

 - Interactive

```{r eval=knitr::is_html_output()}

plotly::ggplotly(gg2)

```



 - Theme Updating (ggplot2 default)


```{r}

theme_set_gg()
ggplot(mtcars) + geom_bar(aes(x = carb, fill = factor(carb)))

```

 - Theme Updating (Atrium default)

```{r}

theme_set_atrium()
ggplot(mtcars) + geom_bar(aes(x = carb, fill = factor(carb)))

theme_set_wake() #and back to wake for future graphics

```
 
 - Font Awesome
 
```{r}

mtcars |> ggplot(aes(x = mpg, y = hp)) +
  geom_fontawesome('head-side-virus', size = 10) +
  labs(title = 'Using a font awesome icon')


mtcars |> 
  mutate(myicon = if_else(am==0, 'robot','user')) |>
  ggplot(aes(x = mpg, y = hp, color = factor(gear), fill = factor(gear))) +
  geom_fontawesome(myicon, size = 10) +
  labs(title = 'Using font awesome icons in dataset') +
  guides(color = guide_legend(override.aes = aes(label = "■"))
         ) #otherwise "a" is in legend

```


## Terms of Use

You should not rely on this Website for medical advice or guidance.

The Website relies upon publicly available data that do not always agree. Authors hereby disclaims any and all representations and warranties with respect to the Website, including accuracy, fitness for use, reliability, completeness, and non-infringement of third party rights.

These terms and conditions are subject to change. Your use of the Website constitutes your acceptance of these terms and conditions and any future modifications thereof.
