---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


<!-- Please keep this updated! You'll need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. -->

```{r}
#| include = FALSE

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {{project_name}}

<!-- badges: start -->
<!-- badges: end -->

The goal of R package `{{project_name}}` is to ...

## Installation

You can install the development version of `{{project_name}}` like so:

``` r
devtools::install_github('wf-id/{{project_name}}')

```

## Shiny App

This package contains a shiny application. This application can be ran like so:

```{r example}
library({{project_name}})
run_app()
```

## Folder structure

The `run_app()` function is located in the R directory, and the shiny application can be found in `inst/shinyapp`.

|-- R
|   |-- run_app.R
|-- inst
|   |-- shinyapp
|       |-- global.R
|       |-- server.R
|       |-- ui.R

